---
title       : BRICS Universities Interactive Chart
author      : Pedro Magalhães Bernardo
job         : February 18, 2017
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
<style>

.title-slide {
  background-color: #FFFFFF;
}
</style>

## Introduction
<br/>
This work is the week 3 assignment for the Data Products course by John Hopkins University on Coursera, as part of their Data Science Specialization.  
<br/>
# BRICS 
<br/>
BRICS is the acronym for an association of five major emerging national economies: Brazil, Russia, India, China and South Africa.  
<br/>
The chart at the end of this presentation aims to compare the Universities from this five countries, featured in the Center for World University Rankings.

---

## Data

The data used comes from the Center for World University Rankings and can be found <a href="https://www.kaggle.com/mylesoneill/world-university-rankings">here</a>.

The comparison performed here takes in account the following features:
  1. Publications
  2. Alumni Employment
  3. Final score
  
It is important to notice that in the original dataset, the features, except the final score, are ranked based, meaning that a lower value means a better rank. To make this analysis more intuitive, the features were scaled from 0 to 100, in which a higher value means a better rank.

--- 

## Chart

```{r, echo=FALSE, message=FALSE, eval=FALSE}
library(plyr)
library(dplyr)
library(plotly)
cwurData <- read.csv("cwurData.csv")

brics <- cwurData %>%
  filter(country %in% c("Brazil", "Russia", "India", "China", "South Africa")) %>%
  select(publications, score, alumni_employment, patents, institution, country) %>%
  group_by(institution, country) %>%
  summarise_each(funs(mean))



scaleFuncMin <- function(x) {
  minX <- min(x)
  for (i in 1:length(x)) {
    if(i==minX){
      x[i] <- 100
    }
    else {
      x[i] <- round((minX/x[i])*100, 2)
    }
  }
  return(x)
}

scaleFuncMax <- function(x) {
  maxX <- max(x)
  for (i in 1:length(x)) {
    if(i==maxX){
      x[i] <- 100
    }
    else {
      x[i] <- round((x[i]/maxX)*100, 2)
    }
  }
  return(x)
}


for (i in 1:ncol(brics)) {
  if(!names(brics[,i]) %in% c("institution", "country","score")){
    brics[,i] <- scaleFuncMin(brics[,i])
  }
  else if(names(brics[,i]) == "score") {
    brics[,i] <- scaleFuncMax(brics[,i])
  }
}


chart <- brics %>%
  plot_ly(y       =    ~publications, 
          x       =    ~score, 
          color   =    ~country, 
          size    =    ~alumni_employment,
          text    =    ~paste("Alumni Employment: ", alumni_employment, 
                              "</br> University: ", institution),
          mode    =    "markers",
          type    =    "scatter",
          marker  =    list(sizeref=0.1, sizemode="area"))

htmlwidgets::saveWidget(chart, "plotly.html")
```

```{r wp, echo=FALSE, warning=FALSE, cache=FALSE, results='asis'}
cat('<iframe src="plotly.html" width=100% height=10% allowtransparency="true"> </iframe>')
```
